---
title: "Activity center models"
author: "Cara"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages, include=FALSE}
library(data.table)
library(broom)
library(tidyverse)
library(effects)
library(ggplot2)
library(plyr)
library(kableExtra)
```

--------------------------------------------------------------------------------

### Preliminary models for analyzing spotted owl activity center ("big grid") data from 2021

### ***NEED TO FINISH THESE WITH QUASIBINOMIAL OR RANDOM EFFECT BC OVERDISPERSED***

--------------------------------------------------------------------------------

#### Load data: 
#####   145 rows = 145 ARU stations from 4 different study areas


```{r, echo=FALSE}
  acData <- fread('../output/05_ac_2021_merged.csv')

## format for a binomial model (each row is an ARU site)
  anySTOC <- acData[,c('STOC_ANY_N','duration','Distance','dist_intended','reproState')]
  fnSTOC  <- acData[,c('STOC_4N_N','duration','Distance','dist_intended','reproState')]
    
## convert to binary (and convert NAs to 0s)
  
  #any STOC detections
  anySTOC$stoc_any <- ifelse(is.na(anySTOC$STOC_ANY_N) | anySTOC$STOC_ANY_N == 0, 0, 1)
    anySTOC$reproState <- factor(anySTOC$reproState, levels = c('pair','nest','fledged'))
    anySTOC[,-1][order(anySTOC$dist_intended),]
    
  #4-note hoots only
  fnSTOC$stoc_fournote <- ifelse(is.na(fnSTOC$STOC_4N_N) | fnSTOC$STOC_4N_N == 0, 0, 1)
    fnSTOC$reproState <- factor(fnSTOC$reproState, levels = c('pair','nest','fledged'))    
    fnSTOC[,-1][order(fnSTOC$dist_intended),]
    
```

####  
#### Then format into groups: 
#####   6 distances * 3 reproductive states = 18 groups

```{r, echo=FALSE}
## Re-format dataframe as Bernoulli (each row is a combo of groups) *using intended distance*

  #any STOC
    anyStocBern <- dcast(anySTOC[,-c(1:2)], dist_intended + reproState ~ stoc_any, 
                         fun.aggregate = length, value.var = 'stoc_any')
    colnames(anyStocBern)[c(3:4)] <- c('No','Yes')
    anyStocBern$reproState <- factor(anyStocBern$reproState, levels = c('pair','nest','fledged'))  
      
  #four-note hoots
    fnStocBern <- dcast(fnSTOC[,-c(1:2)], dist_intended + reproState ~ stoc_fournote,
                        fun.aggregate = length, value.var = 'stoc_fournote')
    colnames(fnStocBern)[c(3:4)] <- c('No','Yes')
    fnStocBern$reproState <- factor(fnStocBern$reproState, levels = c('pair','nest','fledged'))  
      
```

```{r}
## any spotted owl detections
  anyStocBern

## four-note hoot detections only
  fnStocBern

```



### Data summaries by reproductive state and by distance

```{r, echo=FALSE}
  # anySTOC %>%
  #   count(reproState, STOC, sort = TRUE)
  
  anySTOC %>%
    mutate(any_stoc = as_factor(stoc_any)) %>%
    dplyr::count(reproState, stoc_any) %>%
    ggplot(aes(x = reproState, y = n, fill = stoc_any)) +
    geom_col() +
    ylab('number of sites (out of 145)') +
    ylim(0,80)

  fnSTOC %>%
    mutate(fnSTOC = as_factor(stoc_fournote)) %>%
    dplyr::count(reproState, stoc_fournote) %>%
    ggplot(aes(x = reproState, y = n, fill = stoc_fournote)) +
    geom_col() +
    ylab('number of sites (out of 145)') +
    ylim(0,80)
  
  # anySTOC %>%
  #   count(dist_m, STOC, sort = TRUE)
  
  anySTOC %>%
    mutate(STOC = as_factor(stoc_any)) %>%
    dplyr::count(dist_intended, stoc_any) %>%
    ggplot(aes(x = dist_intended, y = n, fill = stoc_any)) +
    geom_col() +
    ylab('number of sites (out of 145)')
  
  fnSTOC %>%
    mutate(STOC = as_factor(stoc_fournote)) %>%
    dplyr::count(dist_intended, stoc_fournote) %>%
    ggplot(aes(x = dist_intended, y = n, fill = stoc_fournote)) +
    geom_col() +
    ylab('number of sites (out of 145)')
  
  # anySTOC %>%
  #   mutate(STOC = as_factor(stoc_any)) %>%
  #   dplyr::count(duration, stoc_any) %>%
  #   ggplot(aes(x = duration, y = n, fill = stoc_any)) +
  #   geom_col() +
  #   ylab('number of sites (out of 145)')
  
```

### --------------------------------------------------------------------------------
###  
### -- Models with any spotted owl detection as response variable
###  
#### 1. effect of reproductive state

```{r}

  any.repro.glm <- glm(cbind(Yes, No) ~ reproState, data = anyStocBern, family = binomial)

    summary(any.repro.glm) #overdispersed (residual deviance >> df)
    
  #use quasibinomial instead  
  any.repro.glm.quasi <- glm(cbind(Yes, No) ~ reproState, data = anyStocBern, family = quasibinomial)  
  
    summary(any.repro.glm.quasi)

  #back-transformed coefficients (probabilities of detecting a spotted owl)
  allEffects(any.repro.glm.quasi)  

```

#### reorder levels so intercept is 'fledged'

```{r}

  anyStocBern2 <- anyStocBern
  anyStocBern2$reproState <- factor(anyStocBern2$reproState, levels = c('fledged','nest','pair'))  

  any.repro.glm.quasi2 <- glm(cbind(Yes, No) ~ reproState, data = anyStocBern2, family = quasibinomial)
  
    summary(any.repro.glm.quasi2)
    
```


```{r, echo=FALSE}

## plot effects above

  #save effects as dataframe
  df.any.repro.glm <- allEffects(any.repro.glm.quasi)
  df.any.repro.glm <- data.frame(df.any.repro.glm$reproState)
  df.any.repro.glm$reproState <- factor(df.any.repro.glm$reproState, levels = c('pair','nest','fledged'))
  
  #and plot
  plot.any.repro.glm <- ggplot(df.any.repro.glm, aes(x = reproState, y = fit)) + 
    geom_point(size = 3) +
    geom_errorbar(aes(ymin = lower, ymax = upper)) +
    ylim(c(0,1)) +
    ylab('probability of spotted owl detection (any)') +
    # ggtitle('Spotted owl detections by reproductive state') +
    theme(panel.background = element_rect(fill = 'transparent'),
          axis.line = element_line(),
          axis.title = element_text(size = 18),
          axis.title.x = element_blank(),
          strip.text = element_text(size = 16),
          axis.text = element_text(size = 16),
          plot.title = element_text(hjust = 0.5),
          legend.text = element_text(size = 16),
          legend.title = element_blank(),
          legend.position = 'none',
          legend.background = element_rect(fill='transparent'))
  plot.any.repro.glm

# plot(allEffects(any.repro.glm))  #for comparison

```


###  
#### 2. effect of distance from center (in meters)

```{r}

  any.dist.glm <- glm(cbind(Yes, No) ~ dist_intended, data = anyStocBern, family = binomial)

    summary(any.dist.glm)  #overdispersed, use quasibinomial
    
  any.dist.glm.quasi <- glm(cbind(Yes, No) ~ dist_intended, data = anyStocBern, family = quasibinomial)
  
    summary(any.dist.glm.quasi)
    
  #back-transformed coefficients (probabilities of detecting a spotted owl)
  allEffects(any.dist.glm.quasi) 
    
```

```{r, echo=FALSE}

## plot effects above

  #save effects as dataframe
  df.any.dist.glm <- allEffects(any.dist.glm.quasi)
  df.any.dist.glm <- data.frame(df.any.dist.glm$dist_intended)

  #and plot
  plot.any.dist.glm <- ggplot(df.any.dist.glm, aes(x = dist_intended/1000, y = fit)) + 
    # geom_point(size = 3) +
    # geom_errorbar(aes(ymin = lower, ymax = upper)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.3) +
    # geom_smooth() +
  # ggplot(stocBern, aes(x = dist_m, y = Yes)) +
  # geom_smooth(data = stocBern, formula = cbind(Yes, No) ~ dist_m,
  #             method = "glm", colour = "black", linetype = 2, fill = "gray80", alpha = 0.2,
  #             method.args = list(family = binomial)) +
    geom_line() +
    ylim(c(0,1)) +
    ylab('probability of spotted owl detection (any)') +
    xlab('Distance from center (km)') +
    # ggtitle('Spotted owl detections by reproductive state') +
    theme(panel.background = element_rect(fill = 'transparent'),
          axis.line = element_line(),
          axis.title = element_text(size = 18),
          # axis.title.x = element_blank(),
          strip.text = element_text(size = 16),
          axis.text = element_text(size = 16),
          plot.title = element_text(hjust = 0.5),
          legend.text = element_text(size = 16),
          legend.title = element_blank(),
          legend.position = 'none',
          legend.background = element_rect(fill='transparent'))
  plot.any.dist.glm

# plot(allEffects(any.dist.glm))  #for comparison

```


###  
#### 3. interaction of reproState * distance

```{r}

  any.repro.dist.glm <- glm(cbind(Yes, No) ~ reproState * dist_intended, data = anyStocBern, family = binomial)

    sumary(any.repro.dist.glm) #overdispersed, use quasibinomial

  any.repro.dist.glm.quasi <- glm(cbind(Yes, No) ~ reproState * dist_intended, data = anyStocBern, 
                                  family = quasibinomial)
  
    summary(any.repro.dist.glm.quasi)
  
  #effects -- back-transformed coefficients (probabilities of detection)
  allEffects(any.repro.dist.glm.quasi)  
  
```

```{r, echo=FALSE}

## plot effects above

  #save effects as dataframe
  df.any.repro.dist.glm <- allEffects(any.repro.dist.glm.quasi)
  df.any.repro.dist.glm <- data.frame(df.any.repro.dist.glm$`reproState:dist_intended`)
  
  df.any.repro.dist.glm$reproState <- factor(df.any.repro.dist.glm$reproState, 
                                             levels = c('pair','nest','fledged'))

  #and plot
  plot.any.repro.dist.glm <- ggplot(df.any.repro.dist.glm, aes(x = dist_intended/1000, y = fit)) + 
    # geom_point(size = 3) +
    # geom_errorbar(aes(ymin = lower, ymax = upper)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.3) +
    geom_line() +
    # geom_smooth() +
    facet_grid(~reproState) +
    ylim(c(0,1)) +
    ylab('probability of spotted owl detection (any)') +
    xlab('Distance from center (km)') +
    # ggtitle('Spotted owl detections by reproductive state') +
    theme(panel.background = element_rect(fill = 'transparent'),
          axis.line = element_line(),
          axis.title = element_text(size = 18),
          # axis.title.x = element_blank(),
          strip.text = element_text(size = 16),
          axis.text = element_text(size = 16),
          plot.title = element_text(hjust = 0.5),
          legend.text = element_text(size = 16),
          legend.title = element_blank(),
          legend.position = 'none',
          legend.background = element_rect(fill='transparent'))
  plot.any.repro.dist.glm
  
  # plot(allEffects(any.repro.dist.glm)) #for comparison
  
```


###  
#### -- compare models using AIC -- can't do AIC with quasibinomial

```{r, echo=FALSE}

## Compare models
  mods.aic <- data.frame('model' = c('null','reproState','distance','reproState*dist'),
                         'AIC' = c(AIC(glm(cbind(Yes, No) ~ 1, data = anyStocBern, family = binomial)),
                                   AIC(any.repro.glm), 
                                   AIC(any.dist.glm),
                                   AIC(any.repro.dist.glm)))
  mods.aic <- mods.aic[order(mods.aic$AIC),]  
  mods.aic$delta_AIC <- mods.aic$AIC - mods.aic$AIC[1]
  
                         
  mods.aic %>%
    kbl(digits = 3) %>%
    kable_styling(bootstrap_options = 'striped', font_size = 14, full_width = FALSE, position = 'left')
  

```

### --------------------------------------------------------------------------------

###  
### -- Models with spotted owl 4-note hoot detections as response variable
###  
#### 1. effect of reproductive state

```{r}

  fn.repro.glm <- glm(cbind(Yes, No) ~ reproState, data = fnStocBern, family = binomial)

    tidy(fn.repro.glm)

  #back-transformed coefficients (probabilities of detecting a spotted owl)
  allEffects(fn.repro.glm)  

```

#### reorder levels so intercept is 'fledged'

```{r}

  fnStocBern2 <- fnStocBern
  fnStocBern2$reproState <- factor(fnStocBern2$reproState, levels = c('fledged','nest','pair'))  

  fn.repro.glm.2 <- glm(cbind(Yes, No) ~ reproState, data = fnStocBern2, family = binomial)
  
    tidy(fn.repro.glm.2)
    
```


```{r, echo=FALSE}

## plot effects above

  #save effects as dataframe
  df.fn.repro.glm <- allEffects(fn.repro.glm)
  df.fn.repro.glm <- data.frame(df.fn.repro.glm$reproState)
  df.fn.repro.glm$reproState <- factor(df.fn.repro.glm$reproState, levels = c('pair','nest','fledged'))
  
  #and plot
  plot.fn.repro.glm <- ggplot(df.fn.repro.glm, aes(x = reproState, y = fit)) + 
    geom_point(size = 3) +
    geom_errorbar(aes(ymin = lower, ymax = upper)) +
    ylim(c(0,1)) +
    ylab('probability of spotted owl detection (4-note)') +
    # ggtitle('Spotted owl detections by reproductive state') +
    theme(panel.background = element_rect(fill = 'transparent'),
          axis.line = element_line(),
          axis.title = element_text(size = 18),
          axis.title.x = element_blank(),
          strip.text = element_text(size = 16),
          axis.text = element_text(size = 16),
          plot.title = element_text(hjust = 0.5),
          legend.text = element_text(size = 16),
          legend.title = element_blank(),
          legend.position = 'none',
          legend.background = element_rect(fill='transparent'))
  plot.fn.repro.glm

# plot(allEffects(fn.repro.glm))  #for comparison

```


###  
#### 2. effect of distance from center (in meters)

```{r}

  fn.dist.glm <- glm(cbind(Yes, No) ~ dist_intended, data = fnStocBern, family = binomial)

    tidy(fn.dist.glm)
    
  #back-transformed coefficients (probabilities of detecting a spotted owl)
  allEffects(fn.dist.glm) 
    
```

```{r, echo=FALSE}

## plot effects above

  #save effects as dataframe
  df.fn.dist.glm <- allEffects(fn.dist.glm)
  df.fn.dist.glm <- data.frame(df.fn.dist.glm$dist_intended)

  #and plot
  plot.fn.dist.glm <- ggplot(df.fn.dist.glm, aes(x = dist_intended/1000, y = fit)) + 
    geom_point(size = 3) +
    geom_errorbar(aes(ymin = lower, ymax = upper)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.3) +
    # geom_smooth() +
  # ggplot(stocBern, aes(x = dist_m, y = Yes)) +
  # geom_smooth(data = stocBern, formula = cbind(Yes, No) ~ dist_m,
  #             method = "glm", colour = "black", linetype = 2, fill = "gray80", alpha = 0.2,
  #             method.args = list(family = binomial)) +
    geom_line() +
    ylim(c(0,1)) +
    ylab('probability of spotted owl detection (4-note)') +
    xlab('Distance from center (km)') +
    # ggtitle('Spotted owl detections by reproductive state') +
    theme(panel.background = element_rect(fill = 'transparent'),
          axis.line = element_line(),
          axis.title = element_text(size = 18),
          # axis.title.x = element_blank(),
          strip.text = element_text(size = 16),
          axis.text = element_text(size = 16),
          plot.title = element_text(hjust = 0.5),
          legend.text = element_text(size = 16),
          legend.title = element_blank(),
          legend.position = 'none',
          legend.background = element_rect(fill='transparent'))
  plot.fn.dist.glm

# plot(allEffects(fn.dist.glm))  #for comparison

```


###  
#### 3. interaction of reproState * distance

```{r}

  fn.repro.dist.glm <- glm(cbind(Yes, No) ~ reproState * dist_intended, data = fnStocBern, family = binomial)

    tidy(fn.repro.dist.glm)
    
  #effects -- back-transformed coefficients (probabilities of detection)
  allEffects(fn.repro.dist.glm)  
  
```

```{r, echo=FALSE}

## plot effects above

  #save effects as dataframe
  df.fn.repro.dist.glm <- allEffects(fn.repro.dist.glm)
  df.fn.repro.dist.glm <- data.frame(df.fn.repro.dist.glm$`reproState:dist_intended`)
  
  df.fn.repro.dist.glm$reproState <- factor(df.fn.repro.dist.glm$reproState, 
                                             levels = c('pair','nest','fledged'))

  #and plot
  plot.fn.repro.dist.glm <- ggplot(df.fn.repro.dist.glm, aes(x = dist_intended/1000, y = fit)) + 
    geom_point(size = 3) +
    geom_errorbar(aes(ymin = lower, ymax = upper)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.3) +
    geom_line() +
    # geom_smooth() +
    facet_grid(~reproState) +
    ylim(c(0,1)) +
    ylab('probability of spotted owl detection (4-note)') +
    xlab('Distance from center (km)') +
    # ggtitle('Spotted owl detections by reproductive state') +
    theme(panel.background = element_rect(fill = 'transparent'),
          axis.line = element_line(),
          axis.title = element_text(size = 18),
          # axis.title.x = element_blank(),
          strip.text = element_text(size = 16),
          axis.text = element_text(size = 16),
          plot.title = element_text(hjust = 0.5),
          legend.text = element_text(size = 16),
          legend.title = element_blank(),
          legend.position = 'none',
          legend.background = element_rect(fill='transparent'))
  plot.fn.repro.dist.glm
  
  # plot(allEffects(fn.repro.dist.glm)) #for comparison
  
```


###  
#### -- compare models using AIC

```{r, echo=FALSE}

## Compare models
  mods.aic <- data.frame('model' = c('null','reproState','distance','reproState*dist'),
                         'AIC' = c(AIC(glm(cbind(Yes, No) ~ 1, data = fnStocBern, family = binomial)),
                                   AIC(fn.repro.glm), 
                                   AIC(fn.dist.glm),
                                   AIC(fn.repro.dist.glm)))
  mods.aic <- mods.aic[order(mods.aic$AIC),]  
  mods.aic$delta_AIC <- mods.aic$AIC - mods.aic$AIC[1]
  
                         
  mods.aic %>%
    kbl(digits = 3) %>%
    kable_styling(bootstrap_options = 'striped', font_size = 14, full_width = FALSE, position = 'left')
  

```


### --------------------------------------------------------------------------------

### -- Models with female/male spotted owl detection as response variable
###  
```{r, echo=FALSE}

## create new dataframes
  sexSTOC <- acData[,c('FEMALE_N','MALE_N','duration','Distance','dist_intended','reproState')]
    
## convert to binary (and convert NAs to 0s)
  sexSTOC$female <- ifelse(is.na(sexSTOC$FEMALE_N) | sexSTOC$FEMALE_N == 0, 0, 1)  
  sexSTOC$male   <- ifelse(is.na(sexSTOC$MALE_N) | sexSTOC$MALE_N == 0, 0, 1)  
  
  # sexSTOC[,-c(1:2)][order(sexSTOC$dist_m),]
    
## re-format dataframe as Bernoulli (each row is a combo of groups)
    femaleSTOC <- dcast(sexSTOC[,c(5:7)], dist_intended + reproState ~ female, 
                        fun.aggregate = length, value.var = 'female')
    colnames(femaleSTOC)[c(3:4)] <- c('No','Yes')
    femaleSTOC$reproState <- factor(femaleSTOC$reproState, levels = c('pair','nest','fledged')) 

    maleSTOC <- dcast(sexSTOC[,c(5:6,8)], dist_intended + reproState ~ male, 
                      fun.aggregate = length, value.var = 'male')
    colnames(maleSTOC)[c(3:4)] <- c('No','Yes')
    maleSTOC$reproState <- factor(maleSTOC$reproState, levels = c('pair','nest','fledged')) #order levels

```

```{r}
## Female spotted owl detections
  femaleSTOC

## Male spotted owl detections
  maleSTOC
```


###  
#### 1. effect of reproductive state (separately for F/M)

```{r}

  #females
  fem.repro.glm <- glm(cbind(Yes, No) ~ reproState, data = femaleSTOC, family = binomial)

    summary(fem.repro.glm) #overdispersed, use quasibinomial insead
  
  #males
  male.repro.glm <- glm(cbind(Yes, No) ~ reproState, data = maleSTOC, family = binomial)  
  
    tidy(male.repro.glm)
    
  #back-transformed coefficients (probabilities of detecting a spotted owl)
  allEffects(fem.repro.glm)
  allEffects(male.repro.glm) 
     
  
```

```{r, echo=FALSE}
## plot

#save effects as dataframe
  df.f.repro.glm <- allEffects(fem.repro.glm)
  df.f.repro.glm <- data.frame(df.f.repro.glm$reproState); df.f.repro.glm$sex <- 'female'

  df.m.repro.glm <- allEffects(male.repro.glm)
  df.m.repro.glm <- data.frame(df.m.repro.glm$reproState); df.m.repro.glm$sex <- 'male'
  
  fm.repro.glm <- rbind(df.f.repro.glm, df.m.repro.glm)
  
  fm.repro.glm$reproState <- factor(fm.repro.glm$reproState,
                                    levels = c('pair','nest','fledged'))
  
  #and plot
  plot.fm.repro.glm <- ggplot(fm.repro.glm, aes(x = reproState, y = fit)) + 
    geom_point(size = 3) +
    geom_errorbar(aes(ymin = lower, ymax = upper)) +
    facet_grid(~sex) +
    ylim(c(0,1)) +
    ylab('probability of spotted owl detection') +
    # ggtitle('Spotted owl detections by reproductive state') +
    theme(panel.background = element_rect(fill = 'transparent'),
          axis.line = element_line(),
          axis.title = element_text(size = 18),
          axis.title.x = element_blank(),
          strip.text = element_text(size = 16),
          axis.text = element_text(size = 16),
          plot.title = element_text(hjust = 0.5),
          legend.text = element_text(size = 16),
          legend.title = element_blank(),
          legend.position = 'none',
          legend.background = element_rect(fill='transparent'))
  plot.fm.repro.glm
  
```


###  
#### 2. effect of distance from center (separately for F/M)

```{r}

  #females
  fem.dist.glm <- glm(cbind(Yes, No) ~ dist_intended, data = femaleSTOC, family = binomial)

    tidy(fem.dist.glm)
    
  #males
  male.dist.glm <- glm(cbind(Yes, No) ~ dist_intended, data = maleSTOC, family = binomial)  
  
    tidy(male.dist.glm)
    
    #effects
    allEffects(fem.dist.glm)
    allEffects(male.dist.glm) 
    
```

```{r, echo=FALSE}
## plot

#save effects as dataframe
  df.f.dist.glm <- allEffects(fem.dist.glm)
  df.f.dist.glm <- data.frame(df.f.dist.glm$dist_intended); df.f.dist.glm$sex <- 'female'

  df.m.dist.glm <- allEffects(male.dist.glm)
  df.m.dist.glm <- data.frame(df.m.dist.glm$dist_intended); df.m.dist.glm$sex <- 'male'

  fm.dist.glm <- rbind(df.f.dist.glm, df.m.dist.glm)

#and plot
  plot.fm.dist.glm <- ggplot(fm.dist.glm, aes(x = dist_intended/1000, y = fit)) + 
    geom_point(size = 3) +
    geom_errorbar(aes(ymin = lower, ymax = upper)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.3) +
    geom_line() +
    facet_grid(~sex) +
    ylim(c(0,1)) +
    ylab('probability of spotted owl detection') +
    xlab('Distance from center (km)') +
    # ggtitle('Spotted owl detections by reproductive state') +
    theme(panel.background = element_rect(fill = 'transparent'),
          axis.line = element_line(),
          axis.title = element_text(size = 18),
          # axis.title.x = element_blank(),
          strip.text = element_text(size = 16),
          axis.text = element_text(size = 16),
          plot.title = element_text(hjust = 0.5),
          legend.text = element_text(size = 16),
          legend.title = element_blank(),
          legend.position = 'none',
          legend.background = element_rect(fill='transparent'))
  plot.fm.dist.glm

```


###  
#### 3. interaction of reproState * distance (separately for F/M)

```{r}

  #females
  fem.repro.dist.glm <- glm(cbind(Yes, No) ~ reproState * dist_intended, data = femaleSTOC, family = binomial)

    tidy(fem.repro.dist.glm)

  #males  
  male.repro.dist.glm <- glm(cbind(Yes, No) ~ reproState * dist_intended, data = maleSTOC, family = binomial)  
  
    tidy(male.repro.dist.glm)
    
    #effects
    allEffects(fem.repro.dist.glm)
    allEffects(male.repro.dist.glm) 
  
    
```

```{r, echo=FALSE}
## plot

#save effects as dataframe
  df.f.repro.dist.glm <- allEffects(fem.repro.dist.glm)
  df.f.repro.dist.glm <- data.frame(df.f.repro.dist.glm$`reproState:dist_intended`)
    df.f.repro.dist.glm$sex <- 'female'

  df.m.repro.dist.glm <- allEffects(male.repro.dist.glm)
  df.m.repro.dist.glm <- data.frame(df.m.repro.dist.glm$`reproState:dist_intended`)
    df.m.repro.dist.glm$sex <- 'male'

  fm.repro.dist.glm <- rbind(df.f.repro.dist.glm, df.m.repro.dist.glm)
  fm.repro.dist.glm$reproState <- factor(fm.repro.dist.glm$reproState,
                                         levels = c('pair','nest','fledged'))

#and plot
  plot.fm.repro.dist.glm <- ggplot(fm.repro.dist.glm, aes(x = dist_intended/1000, y = fit)) + 
    geom_point(size = 3) +
    geom_errorbar(aes(ymin = lower, ymax = upper)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.3) +
    geom_line() +
    facet_grid(rows = vars(sex), cols = vars(reproState)) +
    ylim(c(0,1)) +
    ylab('probability of spotted owl detection') +
    xlab('Distance from center (km)') +
    # ggtitle('Spotted owl detections by reproductive state') +
    theme(panel.background = element_rect(fill = 'transparent'),
          axis.line = element_line(),
          axis.title = element_text(size = 18),
          # axis.title.x = element_blank(),
          strip.text = element_text(size = 16),
          axis.text = element_text(size = 16),
          plot.title = element_text(hjust = 0.5),
          legend.text = element_text(size = 16),
          legend.title = element_blank(),
          legend.position = 'none',
          legend.background = element_rect(fill='transparent'))
  plot.fm.repro.dist.glm


```

###  
###  
#### -- compare models (females)

```{r, echo=FALSE}

## Compare models
  f.mods.aic <- data.frame('sex' = rep('female', 4),
                           'model' = c('null','reproState','distance','reproState*dist'),
                           'AIC' = c(AIC(glm(cbind(Yes, No) ~ 1, data = femaleSTOC, family = binomial)),
                                     AIC(fem.repro.glm), 
                                     AIC(fem.dist.glm),
                                     AIC(fem.repro.dist.glm)))
  f.mods.aic <- f.mods.aic[order(f.mods.aic$AIC),]  
  f.mods.aic$delta_AIC <- f.mods.aic$AIC - f.mods.aic$AIC[1]
  

                         
  f.mods.aic %>%
    kbl(digits = 3) %>%
    kable_styling(bootstrap_options = 'striped', font_size = 14, full_width = FALSE, position = 'left')
  

```

####  
#### -- compare models (males)

```{r, echo=FALSE}

  m.mods.aic <- data.frame('sex' = rep('male', 4),
                           'model' = c('null','reproState','distance','reproState*dist'),
                           'AIC' = c(AIC(glm(cbind(Yes, No) ~ 1, data = maleSTOC, family = binomial)),
                                     AIC(male.repro.glm), 
                                     AIC(male.dist.glm),
                                     AIC(male.repro.dist.glm)))
  m.mods.aic <- m.mods.aic[order(m.mods.aic$AIC),]  
  m.mods.aic$delta_AIC <- m.mods.aic$AIC - m.mods.aic$AIC[1]
  
  m.mods.aic %>%
    kbl(digits = 3) %>%
    kable_styling(bootstrap_options = 'striped', font_size = 14, full_width = FALSE, position = 'left')

```


### --------------------------------------------------------------------------------
###  
### -- Binomial models with any spotted owl detection as response variable (continuous)
###  
#### 1. effect of reproductive state

```{r}

  bin.any.repro.glm <- glm(stoc_any ~ reproState, data = anySTOC, family = binomial)

    tidy(bin.any.repro.glm)

  #back-transformed coefficients (probabilities of detecting a spotted owl)
  allEffects(bin.any.repro.glm)  

```

#### reorder levels so intercept is 'fledged'

```{r}

  anySTOC2 <- anySTOC
  anySTOC2$reproState <- factor(anySTOC2$reproState, levels = c('fledged','nest','pair'))  

  bin.any.repro.glm.2 <- glm(stoc_any ~ reproState, data = anySTOC, family = binomial)
  
    tidy(bin.any.repro.glm.2)
    
```


```{r, echo=FALSE}

## plot effects above

  #save effects as dataframe
  df.bin.any.repro.glm <- allEffects(bin.any.repro.glm)
  df.bin.any.repro.glm <- data.frame(df.bin.any.repro.glm$reproState)
  df.bin.any.repro.glm$reproState <- factor(df.bin.any.repro.glm$reproState, levels = c('pair','nest','fledged'))
  
  #and plot
  plot.bin.any.repro.glm <- ggplot(df.bin.any.repro.glm, aes(x = reproState, y = fit)) + 
    geom_point(size = 3) +
    geom_errorbar(aes(ymin = lower, ymax = upper)) +
    ylim(c(0,1)) +
    ylab('probability of spotted owl detection (any)') +
    theme_bw() +
    # ggtitle('Spotted owl detections by reproductive state') +
    theme(
      # panel.background = element_rect(fill = 'transparent'),
          axis.line = element_line(),
          axis.title = element_text(size = 18),
          axis.title.x = element_blank(),
          strip.text = element_text(size = 16),
          axis.text = element_text(size = 16),
          plot.title = element_text(hjust = 0.5),
          legend.text = element_text(size = 16),
          legend.title = element_blank(),
          legend.position = 'none',
          legend.background = element_rect(fill='transparent'))
  plot.bin.any.repro.glm

# plot(allEffects(bin.any.repro.glm))  #for comparison

```


###  
#### 2. effect of distance from center (in meters)

```{r}

  bin.any.dist.glm <- glm(stoc_any ~ Distance, data = anySTOC, family = binomial)

    tidy(bin.any.dist.glm)
    
  #back-transformed coefficients (probabilities of detecting a spotted owl)
  allEffects(bin.any.dist.glm) 
    
```

```{r, echo=FALSE}

## plot effects above

### try another way
  ggplot(anySTOC, aes(Distance, stoc_any)) + 
  geom_smooth(method = "glm", formula = y ~ x, colour = "black",
              linetype = 2, fill = "gray80", alpha = 0.2,
              method.args = list(family = binomial)) +
  geom_rug(sides = "b") +
  theme_bw() +
  ylab("Probability") + xlab("Distance from center (m)") +
       # title = "Logistic regression model") +
  theme(text = element_text(size = 16),
        plot.margin = margin(50, 50, 50, 50),
        axis.title.x = element_text(vjust = -8),
        axis.title.y = element_text(vjust = 10),
        plot.title = element_text(vjust = 8))

###

 # plot(allEffects(bin.any.dist.glm))  #for comparison

```


###  
#### 3. interaction of reproState * distance

```{r}

  bin.any.repro.dist.glm <- glm(stoc_any ~ reproState * Distance, data = anySTOC, family = binomial)

    tidy(bin.any.repro.dist.glm)
    
  #effects -- back-transformed coefficients (probabilities of detection)
  allEffects(bin.any.repro.dist.glm)  
  
```

```{r, echo=FALSE}

## plot effects above

  #save effects as dataframe
  df.bin.any.repro.dist.glm <- allEffects(bin.any.repro.dist.glm)
  df.bin.any.repro.dist.glm <- data.frame(df.bin.any.repro.dist.glm$`reproState:Distance`)
  
  df.bin.any.repro.dist.glm$reproState <- factor(df.bin.any.repro.dist.glm$reproState, 
                                                 levels = c('pair','nest','fledged'))

  #and plot
  plot.bin.any.repro.dist.glm <- ggplot(df.bin.any.repro.dist.glm, aes(x = Distance/1000, y = fit)) + 
    geom_point(size = 3) +
    geom_errorbar(aes(ymin = lower, ymax = upper)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.3) +
    geom_line() +
    # geom_smooth() +
    facet_grid(~reproState) +
    ylim(c(0,1)) +
    ylab('probability of spotted owl detection (any)') +
    xlab('Distance from center (km)') +
    # ggtitle('Spotted owl detections by reproductive state') +
    theme(panel.background = element_rect(fill = 'transparent'),
          axis.line = element_line(),
          axis.title = element_text(size = 18),
          # axis.title.x = element_blank(),
          strip.text = element_text(size = 16),
          axis.text = element_text(size = 16),
          plot.title = element_text(hjust = 0.5),
          legend.text = element_text(size = 16),
          legend.title = element_blank(),
          legend.position = 'none',
          legend.background = element_rect(fill='transparent'))
  plot.bin.any.repro.dist.glm
  
  # plot(allEffects(any.repro.dist.glm)) #for comparison
  
```


###  
#### -- compare models using AIC

```{r, echo=FALSE}

## Compare models
  mods.aic <- data.frame('model' = c('null','reproState','distance','reproState*dist'),
                         'AIC' = c(AIC(glm(stoc_any ~ 1, data = anySTOC, family = binomial)),
                                   AIC(bin.any.repro.glm), 
                                   AIC(bin.any.dist.glm),
                                   AIC(bin.any.repro.dist.glm)))
  mods.aic <- mods.aic[order(mods.aic$AIC),]  
  mods.aic$delta_AIC <- mods.aic$AIC - mods.aic$AIC[1]
  
                         
  mods.aic %>%
    kbl(digits = 3) %>%
    kable_styling(bootstrap_options = 'striped', font_size = 14, full_width = FALSE, position = 'left')
  

```
