---
title: "Activity center models - counts of detections"
author: "Cara"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages, include=FALSE}
library(data.table)
library(broom)
library(tidyverse)
library(effects)
library(ggplot2)
library(plyr)
library(kableExtra)
library(MASS)
```

--------------------------------------------------------------------------------

### Preliminary models for analyzing spotted owl activity center ("big grid") data from 2021


--------------------------------------------------------------------------------

#### Load data: 
#####   145 rows = 145 ARU stations from 4 different study areas

```{r echo=FALSE}
 
  #import station summary
  acData <- fread('../output/05_ac_2021_merged.csv')
  
  #keep necessary columns
  anySTOC <- acData[,c('STOC_ANY','duration','Distance','dist_intended','reproState')]
  
  #convert NAs to 0s and order levels
  anySTOC$stoc_any_count <- ifelse(is.na(anySTOC$STOC_ANY), 0, anySTOC$STOC_ANY)
  anySTOC$reproState <- factor(anySTOC$reproState, levels = c('pair','nest','fledged'))

  #print
  anySTOC[,c('Distance','reproState','stoc_any_count')][order(anySTOC$Distance)]
  
  #look at distribution of counts
  summary(anySTOC$stoc_any_count)
  hist(anySTOC$stoc_any_count, xlab = 'count')  
    
```

--------------------------------------------------------------------------------

### -- Models using the number of spotted owl detection as the response variable (negative binomial)
###  
#### 1. effect of reproductive state

```{r}

  any.nb.repro <- glm.nb(stoc_any_count ~ reproState, data = anySTOC)
  
    summary(any.nb.repro)
    
  #reorder levels
  anySTOC2 <- anySTOC ; anySTOC2$reproState <- factor(anySTOC2$reproState, levels = c('fledged','nest','pair'))
  any.nb.repro2 <- glm.nb(stoc_any_count ~ reproState, data = anySTOC2)
  
    summary(any.nb.repro2)

  #back-transformed coefficients
  allEffects(any.nb.repro)

```


```{r, echo=FALSE}

## plot effects

  #save effects as dataframe
  df.any.nb.repro <- allEffects(any.nb.repro)
  df.any.nb.repro <- data.frame(df.any.nb.repro$reproState)
  df.any.nb.repro$reproState <- factor(df.any.nb.repro$reproState, levels = c('pair','nest','fledged'))
  
  #and plot
  plot.any.nb.repro <- ggplot(df.any.nb.repro, aes(x = reproState, y = fit)) + 
    geom_point(size = 3) +
    geom_errorbar(aes(ymin = lower, ymax = upper)) +
    # ylim(c(0,0.5)) +
    ylab('Count)') +
    # ggtitle('Spotted owl detections by reproductive state') +
    theme(panel.background = element_rect(fill = 'transparent'),
          panel.grid = element_line(color = 'gray90'),
          axis.line = element_line(),
          axis.title = element_text(size = 18),
          axis.title.x = element_blank(),
          strip.text = element_text(size = 16),
          axis.text = element_text(size = 16),
          plot.title = element_text(hjust = 0.5),
          legend.text = element_text(size = 16),
          legend.title = element_blank(),
          legend.position = 'none',
          legend.background = element_rect(fill='transparent'))
  plot.any.nb.repro

# plot(allEffects(any.prop.repro))  #for comparison

```

###  
###  
#### 2. effect of distance from center

```{r}

  any.nb.dist <- glm.nb(stoc_any_count ~ Distance, data = anySTOC)
  
    summary(any.nb.dist)

  #back-transformed coefficients
  allEffects(any.nb.dist)
  
```

```{r, echo=FALSE}

## plot effects
plot.any.nb.dist <- ggplot(anySTOC, aes(x = Distance/1000, y =stoc_any_count)) +
      geom_point(color = 'gray60') +
      geom_smooth(method = 'glm.nb', formula = y ~ x) +
      geom_rug(sides = 'b', lwd = 1) +
      xlab('Distance from center (km)') + ylab('STOC count') +
      ggtitle('Negative binomial') +
      theme(
        panel.background = element_rect(fill = 'transparent'),
        panel.grid = element_line(color = 'gray90'),
        axis.line = element_line(),
        axis.title = element_text(size = 18),
        # axis.title.x = element_blank(),
        strip.text = element_text(size = 16),
        axis.text = element_text(size = 16),
        plot.title = element_text(hjust = 0.5, size = 18),
        legend.text = element_text(size = 16),
        legend.title = element_blank(),
        legend.position = 'none',
        legend.background = element_rect(fill='transparent'))
plot.any.nb.dist

# plot(allEffects(any.nb.dist))

###

```


###  
#### 3. interaction of reproState * distance

```{r warning=TRUE}

  # any.nb.repro.dist <- glm.nb(stoc_any_count ~ reproState * Distance, data = anySTOC)
  
    # summary(any.nb.repro.dist)

  #back-transformed coefficients
  # allEffects(any.nb.repro.dist)
  
```

###  
#### -- compare models using AIC

```{r, echo=FALSE}

## Compare models
  mods.aic.any <- data.frame('model' = c('null','reproState','distance'),
                             'AIC' = c(AIC(glm.nb(stoc_any_count ~ 1, data = anySTOC)),
                                       AIC(any.nb.repro), 
                                       AIC(any.nb.dist)))
  mods.aic.any <- mods.aic.any[order(mods.aic.any$AIC),]  
  mods.aic.any$delta_AIC <- mods.aic.any$AIC - mods.aic.any$AIC[1]
  
  mods.aic.any %>%
    kbl(digits = 3) %>%
    kable_styling(bootstrap_options = 'striped', font_size = 14, full_width = FALSE, position = 'left')
  

```


### --------------------------------------------------------------------------------

### -- Models using the number of female/male spotted owl detections as the response variable (negative binomial)
###  
```{r, echo=FALSE}

## format counts for females and males

  #keep necessary columns
  fmSTOC <- acData[,c('FEMALE','MALE','duration','Distance','dist_intended','reproState')]
  
  #convert NAs to 0s and order levels
  fmSTOC$count_female <- ifelse(is.na(fmSTOC$FEMALE), 0, fmSTOC$FEMALE)
  fmSTOC$count_male <- ifelse(is.na(fmSTOC$MALE), 0, fmSTOC$MALE)
  fmSTOC$reproState <- factor(fmSTOC$reproState, levels = c('pair','nest','fledged'))

  #print
  fmSTOC[,c('Distance','reproState','count_female','count_male')][order(fmSTOC$Distance)]

  #look at distribution of counts
  
  hist(fmSTOC$count_female, xlab = 'count', main = 'Female')  
    summary(fmSTOC$count_female)
  
  hist(fmSTOC$count_male, xlab = 'count', main = 'Male')   
    summary(fmSTOC$count_male)
    
```


#### 1. effect of reproductive state -- separately for F/M

```{r}

  #females
  fem.nb.repro <- glm.nb(count_female ~ reproState, data = fmSTOC)

    summary(fem.nb.repro)
    
    #reorder levels
    fmSTOC2 <- fmSTOC; fmSTOC2$reproState <- factor(fmSTOC2$reproState, levels = c('fledged','nest','pair'))
    fem.nb.repro2 <- glm.nb(count_female ~ reproState, data = fmSTOC2)
    
      summary(fem.nb.repro2)
  

  #males
  male.nb.repro <- glm.nb(count_male ~ reproState, data = fmSTOC)

    summary(male.nb.repro)
    
    #reorder levels
    male.nb.repro2 <- glm.nb(count_female ~ reproState, data = fmSTOC2)
    
      summary(male.nb.repro2)    

        
  #back-transformed coefficients
  allEffects(fem.nb.repro) 
  allEffects(male.nb.repro) 
  
```


```{r, echo=FALSE}

## plot effects above

#save effects as dataframe
  df.f.repro.nb <- allEffects(fem.nb.repro)
  df.f.repro.nb <- data.frame(df.f.repro.nb$reproState); df.f.repro.nb$sex <- 'female'

  df.m.repro.nb <- allEffects(male.nb.repro)
  df.m.repro.nb <- data.frame(df.m.repro.nb$reproState); df.m.repro.nb$sex <- 'male'
  
  fm.repro.nb <- rbind(df.f.repro.nb, df.m.repro.nb)
  
  fm.repro.nb$reproState <- factor(fm.repro.nb$reproState, levels = c('pair','nest','fledged'))
  
  #and plot
  plot.fm.repro.nb <- ggplot(fm.repro.nb, aes(x = reproState, y = fit)) + 
      geom_point(size = 3) +
      geom_errorbar(aes(ymin = lower, ymax = upper)) +
      facet_grid(~sex) +
      # ylim(c(0,1)) +
      ylab('Probability') +
      # scale_color_manual(values = c('tomato1', 'steelblue2', 'seagreen')) +
      # ggtitle('Spotted owl detections by reproductive state') +
      theme(panel.background = element_rect(fill = 'transparent'),
            panel.grid = element_line(color = 'gray90'),
            axis.line = element_line(),
            axis.title = element_text(size = 18),
            axis.title.x = element_blank(),
            strip.text = element_text(size = 16),
            axis.text = element_text(size = 16),
            plot.title = element_text(hjust = 0.5),
            legend.text = element_text(size = 16),
            legend.title = element_blank(),
            legend.position = 'none',
            legend.background = element_rect(fill='transparent'))
    plot.fm.repro.nb

# plot(allEffects(fem.prop.repro))  #for comparison
# plot(allEffects(male.prop.repro))  #for comparison

```

###  
#### 2. effect of distance from center -- separately for F/M

```{r}

  #females
  fem.nb.dist <- glm.nb(count_female ~ Distance, data = fmSTOC)
  
    summary(fem.nb.dist)

  #males
  male.nb.dist <- glm.nb(count_male ~ Distance, data = fmSTOC)  
  
    summary(male.nb.dist)
    
    #effects
    allEffects(fem.nb.dist)
    allEffects(male.nb.dist) 

```

```{r, echo=FALSE}

## plot effects

  #create longform dataframe
  fmLong <- melt(fmSTOC[,c('Distance','reproState','count_female','count_male')], 
                 id.vars = c('Distance','reproState'), value.name = 'count', variable.name = 'sex')


  #and plot
  plot.fm.nb.dist <- ggplot(fmLong, aes(x = Distance/1000, y = count, color = sex, fill = sex)) +
      geom_point(data = fmLong[fmLong$sex %in% 'count_male',], alpha = 0.3) +
      geom_point(data = fmLong[fmLong$sex %in% 'count_female',], alpha = 0.3) +
      geom_smooth(data = fmLong[fmLong$sex %in% 'count_male',],
                  method = 'glm.nb', formula = y ~ x) +
      geom_smooth(data = fmLong[fmLong$sex %in% 'count_female',],
                  method = 'glm.nb', formula = y ~ x) +
      geom_rug(data = fmLong[fmLong$sex %in% 'count_male' & fmLong$count > 0,], 
               color = 'cyan4', sides = "b", outside = TRUE) +
      geom_rug(data = fmLong[fmLong$sex %in% 'count_female' & fmLong$count > 0,], 
               color = 'tomato1', sides = "b") +
      # scale_color_manual(values = c('cyan4','tomato1')) +
      coord_cartesian(clip = "off") +
      xlab('Distance from center (km)') + ylab('STOC count') +
      ggtitle('Negative binomial') +
        theme(
          panel.background = element_rect(fill = 'transparent'),
          panel.grid = element_line(color = 'gray90'),
          axis.line = element_line(),
          axis.title = element_text(size = 18),
          # axis.title.x = element_blank(),
          strip.text = element_text(size = 16),
          axis.text = element_text(size = 16),
          plot.title = element_text(hjust = 0.5, size = 18),
          legend.text = element_text(size = 16),
          legend.title = element_blank(),
          # legend.position = 'none',
          legend.background = element_rect(fill='transparent'))
  plot.fm.nb.dist
 
    

# plot(allEffects(fem.nb.dist))
# plot(allEffects(male.nb.dist))

```


###  
#### 3. interaction of reproState * distance

```{r}

  #females
  # fem.nb.repro.dist <- glm.nb(count_female ~ reproState * Distance, data = fmSTOC)
  # 
  #   summary(fem.nb.repro.dist)
  # 
  #   #reorder levels
  #   fem.nb.repro.dist2 <- glm.nb(count_female ~ reproState * Distance, data = fmSTOC2)
  # 
  #     summary(fem.nb.repro.dist)
  #   
  #males
  # male.nb.repro.dist <- glm.nb(count_male ~ reproState * Distance, data = fmSTOC)
  # 
  #   summary(male.nb.repro.dist)
  # 
  #   #reorder levels
  #   male.nb.repro.dist2 <- glm.nb(count_male ~ reproState * Distance, data = fmSTOC2)
  # 
  #     summary(male.nb.repro.dist2)


  #back-transformed coefficients
  # allEffects(fem.nb.repro.dist)
  # allEffects(male.nb.repro.dist)
  
```

```{r, echo=FALSE}

## plot 

    
```


###  
#### -- compare models (females)

```{r, echo=FALSE}

## Compare models

  #female
  mods.aic.f <- data.frame('model' = c('null','reproState','distance'),
                           'AIC' = c(AIC(glm.nb(count_female ~ 1, data = fmSTOC)),
                                     AIC(fem.nb.repro), 
                                     AIC(fem.nb.dist)))
  mods.aic.f <- mods.aic.f[order(mods.aic.f$AIC),]  
  mods.aic.f$delta_AIC <- mods.aic.f$AIC - mods.aic.f$AIC[1]
  
                         
  mods.aic.f %>%
    kbl(digits = 3) %>%
    kable_styling(bootstrap_options = 'striped', font_size = 14, full_width = FALSE, position = 'left')
  

```

#### -- compare models (males)
```{r, echo=FALSE}

## Compare models

  #male
  mods.aic.m <- data.frame('model' = c('null','reproState','distance'),
                           'AIC' = c(AIC(glm.nb(count_male ~ 1, data = fmSTOC)),
                                     AIC(male.nb.repro), 
                                     AIC(male.nb.dist)))
  mods.aic.m <- mods.aic.m[order(mods.aic.m$AIC),]  
  mods.aic.m$delta_AIC <- mods.aic.m$AIC - mods.aic.m$AIC[1]
  
                         
  mods.aic.m %>%
    kbl(digits = 3) %>%
    kable_styling(bootstrap_options = 'striped', font_size = 14, full_width = FALSE, position = 'left')
```


##